---
title: "R Notebook"
output: html_notebook
---

New Seurat analysis on full 25K data set - adapted from tutorial provided at: https://satijalab.org/seurat/v3.0/pbmc3k_tutorial.html

```{r}
library(Seurat)
library(dplyr)
library(cowplot)
library(data.table)
```


```{r}
data_dir <- '/home/cpalmateer/Desktop/Cellranger/outs/filtered_gene_bc_matrices/dm6SCGFPNEW'
list.files(data_dir)
Full25K <- Read10X(data.dir = data_dir)
Full25K <- CreateSeuratObject(counts = Full25K, min.cells = 3, min.features = 200, 
                           project = "48hrAPF")
```

Prefiletering and QC on all the cells 

```{r fig.height=5, fig.width=8}
Full25K[["percent.mt"]] <- PercentageFeatureSet(Full25K, pattern = "mt")
VlnPlot(Full25K, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"),pt.size=0, ncol=3)
```
```{r fig.height=5, fig.width=8}
VlnPlot(Full25K, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol=3)
```

Using these QC metrics, I'll filter out cells

    
```{r fig.height=5, fig.width=15}
plot1 <- FeatureScatter(Full25K, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(Full25K, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

CombinePlots(plots = list(plot1, plot2))
```

    We filter cells that have unique feature counts over 6000 or less than 200
    We filter cells that have >5% mitochondrial counts


```{r}
Full25K <- subset(Full25K, subset = nFeature_RNA > 200 & nFeature_RNA < 6000 & percent.mt < 5)
Full25K
```
24,902 total cells

```{r fig.height=5, fig.width=15}
plot1 <- FeatureScatter(Full25K, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
plot1
```
Very good agreement 


Now how many are GFP positive and therefore fru P1-expressing cells?
```{r}
GFPcells<- SubsetData(Full25K,subset.name="GFP", assay = NULL,cells= NULL, low.threshold = 0)
GFPcells
```
5,621 GFP positive cells - fru P1-expressing cells

-----------------------------
Now to subset out the GFP positve cells
```{r}
GFPcells <- SubsetData(Full25K,subset.name="GFP", assay = NULL,cells= NULL, low.threshold = 0)
GFPcells
```


Now I'll run normalization and scaling steps on the GFP expressing cells
```{r}
GFPcells <- NormalizeData(GFPcells, normalization.method = "LogNormalize", scale.factor = 10000)
```


Identification of highly variable features (feature selection)

We next calculate a subset of features that exhibit high cell-to-cell variation in the dataset (i.e, they are highly expressed in some cells, and lowly expressed in others). 

```{r}
GFPcells <- FindVariableFeatures(GFPcells, selection.method = "vst", nfeatures = 2000)
```

```{r}
# Identify the 10 most highly variable genes
top10GFP <- head(VariableFeatures(GFPcells), 10)
# plot variable features with and without labels
plot1GFP <- VariableFeaturePlot(GFPcells)
plot2GFP <- LabelPoints(plot = plot1GFP, points = top10GFP, repel = TRUE)
CombinePlots(plots = list(plot1GFP, plot2GFP))
```

Scaling the data

Next, we apply a linear transformation (‘scaling’) that is a standard pre-processing step prior to dimensional reduction techniques like PCA. The ScaleData function:

    Shifts the expression of each gene, so that the mean expression across cells is 0
    Scales the expression of each gene, so that the variance across cells is 1
        This step gives equal weight in downstream analyses, so that highly-expressed genes do not dominate
        
```{r}
all.genesGFP <- rownames(GFPcells)
GFPcells <- ScaleData(GFPcells, features = all.genesGFP)
```




Pull expression table for dprs/DIPs 
```{r}
include_list <- c("dpr1", "dpr2", "dpr3", "dpr4", "dpr5", 
                  "dpr6", "dpr7", "dpr8", "dpr9", "dpr10", "dpr11", 
                  "dpr12", "dpr13", "dpr14", "dpr15", "dpr16", "dpr17", "dpr18", 
                  "dpr19", "dpr20","dpr21", "DIP-alpha", "DIP-beta", "DIP-gamma", "DIP-delta", "DIP-epsilon", "DIP-zeta"
                  , "DIP-eta", "DIP-iota", "DIP-theta", "cDIP", "CG45781", "CG31814")
```

Now I want to write out spreadsheets - supplemenrary table 6, sheet 2:

```{r}
#get the list of GFP cells only
data_to_write_out2 <- as.data.frame(as.matrix(GFPcells[["RNA"]]@scale.data))
GFPcellsdprDIP<-subset(data_to_write_out2, rownames(data_to_write_out2) %in% include_list)
fwrite(x = GFPcellsdprDIP, row.names = TRUE, file = "GFPcellsdprDIP_manuscale.csv")
```

Save seurat object for downstream analyses
```{r}
saveRDS(GFPcells, file = "GFPcells.rds")
```


























