---
title: "DprDIP fru P1 cell analysis PCA and Cluster"
output: html_notebook
---

Now for the dpr/DIP analysis. So we'll use these as our PCs.

```{r}
library(Seurat)
library(dplyr)
library(cowplot)
library(data.table)
```


```{r}
PCgenes<-as.character(c("dpr1", "dpr2", "dpr3", "dpr4", "dpr5", 
                  "dpr6", "dpr7", "dpr8", "dpr9", "dpr10", "dpr11", 
                  "dpr12", "dpr13", "dpr14", "dpr15", "dpr16", "dpr17", "dpr18", 
                  "dpr19", "dpr20","dpr21", "DIP-alpha", "DIP-beta", "DIP-gamma", "DIP-delta", "DIP-epsilon", "DIP-zeta"
                  , "DIP-eta", "DIP-iota", "DIP-theta", "cDIP", "CG45781", "CG31814"))
```


Read in fru P1, GFP-expressing cell seurat object

```{r}
GFPcells<-readRDS ("~/Documents/Colleen's R-Notebooks/GFPcells.rds")
```


Run PCA dimentional reduction on only dpr/DIPs instead of highly variable genes


```{r}
dprDIPGFP<- RunPCA(GFPcells, features = PCgenes, npcs = 32)
```

Evaluate PC heatmaps
```{r fig.height=25, fig.width=25}
DimHeatmap(dprDIPGFP, dims = 1:32, cells = 500, balanced = TRUE)
```

Visualize elbow plot

```{r}
ElbowPlot(dprDIPGFP, ndims=32)
```


Cluster
```{r}
dprDIPGFP <- FindNeighbors(dprDIPGFP, dims = 1:20)
dprDIPGFP <- FindClusters(dprDIPGFP, resolution = c(0.5,0.6,0.7,1,1.3,1.5,1.7,2,2.5))
```

Run UMAP
```{r}
dprDIPGFP <- RunUMAP(dprDIPGFP, dims = 1:20)
```

Generate the UMAP plot

Figure 10A
```{r}
Idents(dprDIPGFP) <- "RNA_snn_res.1.3"
DimPlot(dprDIPGFP, reduction = "umap")
```



Feature plots with dpr/DIP expression overlayed

Supplementary figure 5
```{r fig.height=30, fig.width=15}
FeaturePlot(dprDIPGFP, features = c("dpr1", "dpr2", "dpr3", "dpr4", "dpr5", 
                  "dpr6", "dpr7", "dpr8", "dpr9", "dpr10", "dpr11", 
                  "dpr12", "dpr13", "dpr14", "dpr15", "dpr16", "dpr17", "dpr18", 
                  "dpr19", "dpr20","dpr21","DIP-alpha", "DIP-beta", "DIP-gamma", "DIP-delta", "DIP-epsilon", "DIP-zeta"
                  , "DIP-eta", "DIP-iota", "DIP-theta", "cDIP", "CG45781", "CG31814"), cols=c("lightgrey", "purple"))
```

Dotplot analysis for dpr/DIPs for GFP expressing cells

Figure 10 B
```{r}
DotPlot(object = dprDIPGFP, feature = c("CG45781", "CG31814", "DIP-iota", "DIP-theta", "DIP-eta", "DIP-zeta", "DIP-epsilon", "DIP-delta","DIP-gamma", "DIP-beta", "DIP-alpha", "dpr21", 
"dpr20","dpr19", "dpr18", "dpr17", "dpr16", "dpr15", "dpr14","dpr13", "dpr12", "dpr11", "dpr10", "dpr9", "dpr8", "dpr7", "dpr6", "dpr5", "dpr4",
"dpr3", "dpr2", "dpr1")) + RotatedAxis()
```



```{r}
print(sessionInfo())
```












