---
title: "dprs/DIPs 48hr APF single cell Upset"
output: html_notebook
---

Scaled data analysis using data from Supplemtary table S6, sheet 2

```{r}
library(UpSetR)
library(data.table)
```

Read in the table and transpose the single cell matrix
```{r}
GFPcells<- read.table(file="~/Desktop/GFPcellsdprDIP_manuscale.csv", header=TRUE, sep=",")
GFPcellsT = setNames(data.frame(t(GFPcells[,-1])), GFPcells[,1])
```

Now I have to export the data.frame out and read it back in to get my headers back.
```{r}
fwrite(x = GFPcellsT, row.names = TRUE, file = "GFPcellsdprDIPManuscriptscaleT.csv")
```

Bring it back in so all cell names are put into their own column 
```{r}
GFPcellsT1<- read.table(file="~/Desktop/GFPcellsdprDIPManuscriptscaleT.csv", header=TRUE, sep=",")
```

Now, I need to binarize the expression matrix, anything with a value over 0 is converted to a "1"
```{r}
GFPcellsT1[GFPcellsT1 > 1] = 1
GFPcellsT1[GFPcellsT1 < 1] = 0
```


Now ask how many cells do not have any dpr/DIPs with at least one dpr/DIP expressed based on these criteria
```{r}
mydatanew=GFPcellsT1[,-1] 
nonzero_row <- mydatanew[rowSums(mydatanew) > 0, ]
dim(nonzero_row)
```

This narrows out 403 cells. 

Now lets overwrite and rename the object to GFPcells for similicity.
```{r}
GFPcells<-GFPcellsT1
```

Export the binary data

I have to export the data.frame out and read it back in to get my headers back.
```{r}
fwrite(x = GFPcells, row.names = TRUE, file = "GFPcellsdprDIPManuscriptBinaryscale.csv")
```

Make the Upset plot to ask about dpr/DIP expression combinations 

```{r fig.height=15, fig.width=25}
upset(GFPcells, sets = c("dpr1", "dpr2", "dpr3", "dpr4", "dpr5", 
                  "dpr6", "dpr7", "dpr8", "dpr9", "dpr10", "dpr11", 
                  "dpr12", "dpr13", "dpr14", "dpr15", "dpr16", "dpr17", "dpr18", 
                  "dpr19", "dpr20","dpr21", "DIP.alpha", "DIP.beta", "DIP.gamma", "DIP.delta", "DIP.epsilon", "DIP.zeta"
                  , "DIP.eta", "DIP.iota", "DIP.theta", "cDIP", "CG31814", "CG45781"),order.by = "freq", set_size.show = TRUE, nintersects = 250)
```

923 cells have a shared expression combo.


```{r}
print(sessionInfo())
```
